First paper - Draft

### 2017-06-17 paper/paper.Rnw
Updated paper code - ran paper and everything worked

<<working directory, echo = F>>=
opts_knit$set(root.dir = '..')

@@

<<modeling>>=
adapted_year_data <-
    map(pisa_all2$value, ~ {
      if (unique(.x$wave) == "pisa2000") {
        # pisa2000 has a different coding so here I recode 6 to 7 so that in all waves the top edu
        # is 7 and the bottom is 1
        .x <-
          mutate(.x, new_hisced = as.character(dplyr::recode(as.numeric(high_edu_broad), `6` = 7)))
      } else {
        .x <-
          mutate(.x, new_hisced = as.character(high_edu_broad))
      }
      .x
})

# results_math <- test_diff(adapted_year_data, reliability_pisa, "MATH")
# results_read <- test_diff(adapted_year_data, reliability_pisa, "READ")
# results_math_topmid <- test_diff(adapted_year_data, reliability_pisa, "MATH", c(0.5, 0.9))
# results_read_topmid <- test_diff(adapted_year_data, reliability_pisa, "READ", c(0.5, 0.9))
# results_math_midbottom <- test_diff(adapted_year_data, reliability_pisa, "MATH", c(0.1, 0.5))
# results_read_midbottom <- test_diff(adapted_year_data, reliability_pisa, "READ", c(0.1, 0.5))

results_math <- read_rds("./data/delete.Rdata")
results_read <- read_rds("./data/delete_read.Rdata")
results_math_topmid <- read_rds("./data/delete_math_topmid.Rdata")
results_read_topmid <- read_rds("./data/delete_read_topmid.Rdata")
results_math_midbottom <- read_rds("./data/delete_math_midbottom.Rdata")
results_read_midbottom <- read_rds("./data/delete_read_midbottom.Rdata")
# US is missing for reading

@@

% Figure out how to ouput data frames as latex tables.
<<sample_size>>=

@@

<<merge_math_read>>=

@@

% How to output data frames are latex tables?
<<rate_change>>=

@@

full_data <-
  left_join(avg_sd_increase_high, avg_sd_increase_low, by = "country") %>%
  mutate(continent = ifelse(country %in% countries, "my_cnt", "other_cnt"))

@@

% How to output data frames are latex tables?
<<perc_increase_tables>>=

>>>>

<<working directory, echo = F>>=
# opts_knit$set(root.dir = '..')

@@

<<modeling, cache = TRUE>>=
adapted_year_data <-
    map(pisa_all2$value, ~ {
      if (unique(.x$wave) == "pisa2000") {
        # pisa2000 has a different coding so here I recode 6 to 7 so that in all waves the top edu
        # is 7 and the bottom is 1
        .x <-
          mutate(.x, new_hisced = as.character(dplyr::recode(as.numeric(high_edu_broad), `6` = 7)))
      } else {
        .x <-
          mutate(.x, new_hisced = as.character(high_edu_broad))
      }
      .x
})

results_math <- test_diff(adapted_year_data, reliability_pisa, "MATH", c(0.1, 0.9))
results_read <- test_diff(adapted_year_data, reliability_pisa, "READ", c(0.1, 0.9))
results_math_topmid <- test_diff(adapted_year_data, reliability_pisa, "MATH", c(0.5, 0.9))
results_read_topmid <- test_diff(adapted_year_data, reliability_pisa, "READ", c(0.5, 0.9))
results_math_midbottom <- test_diff(adapted_year_data, reliability_pisa, "MATH", c(0.1, 0.5))
results_read_midbottom <- test_diff(adapted_year_data, reliability_pisa, "READ", c(0.1, 0.5))

# results_math <- read_rds("./data/delete.Rdata")
# results_read <- read_rds("./data/delete_read.Rdata")
# results_math_topmid <- read_rds("./data/delete_math_topmid.Rdata")
# results_read_topmid <- read_rds("./data/delete_read_topmid.Rdata")
# results_math_midbottom <- read_rds("./data/delete_math_midbottom.Rdata")
# results_read_midbottom <- read_rds("./data/delete_read_midbottom.Rdata")
# US is missing for reading

@@

% Figure out how to ouput data frames as latex tables.
<<sample_size, cache = TRUE>>=

@@

<<merge_math_read, cache = TRUE>>=

@@

% How to output data frames are latex tables?
<<rate_change, cache = TRUE>>=

@@

full_data <-
  left_join(select(avg_sd_increase_high, name, mean),
            select(avg_sd_increase_low, name, mean), by = "name") %>%
  mutate(continent = ifelse(name %in% countries, "my_cnt", "other_cnt"))

@@

% How to output data frames are latex tables?
<<perc_increase_tables, cache = TRUE>>=

### 2017-06-17 paper/paper.tex
Updated paper code - ran paper and everything worked

{\centering \includegraphics[width=5.5in,height=5in]{figure/graphin_differences-1}

@@

{\centering \includegraphics[width=5.5in,height=5in]{figure/unnamed-chunk-2-1}

@@

>>>>

% This chunk needs to have cache = TRUE once you want to run it for like 2 hours until 
% the results_* models have been created once and the cache can save them

% Figure out how to ouput data frames as latex tables.

{\centering \includegraphics[width=5.5in,height=5in]{figure/correlation_incomeineq-1}

@@

{\centering \includegraphics[width=5.5in,height=5in]{figure/graphing_9010gaps-1}

@@

{\centering \includegraphics[width=5.5in,height=5in]{figure/graphing_allgaps-1}

{\centering \includegraphics[width=5.5in,height=5in]{figure/graphing_ses_growth-1}

% How to output data frames are latex tables?

{\centering \includegraphics[width=5.5in,height=5in]{figure/rate_change_graph-1}

% How to output data frames are latex tables?
